Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-30 paper/main.tex
not my finest work, but probably still better?

\begin{figure*}[hbtp]
\centering
\caption{Regular Expression Rule Examples \clg{Comby, or PPC, you think?}}
\label{tab:rules}
  \begin{tabular}{ll|ll|ll}
    \hline
    \mc{2}{c|}{Universal}                          & \mc{2}{c|}{C-Like}      & \mc{2}{c|}{Language-Specific} \\
    Regexp & Comby                                 & Regexp & Comby & Regexp & Comby     \\
    {\lstinline|< ==> >|} & {\lstinline|:[a]<:[b] ==> :[a]>:[b]|}  &  {\lstinline|else ==>|}  & {\lstinline|else ==>|} & {\lstinline|synchronized ==>|} &  {\lstinline|synchronized ==>|} \\
   {\lstinline|< ==> ==|} & {\lstinline|:[a]<:[b] ==> :[a]==:[b]|} &  {\lstinline|if (\(.*\)) ==> if (!\1)|} &  {\lstinline|if (:[cond]) ==> if (!(:[cond]))|} & {\lstinline|(\^{}\s*)(\S+.*\n) ==> \1pass|} & {\lstinline|:[ s]:[expr]:[lf~[\n]] ==> :[s]pass:[lf]|} \\
{\lstinline|< ==> <=|}  & {\lstinline|:[a]<:[b] ==> :[a]<=:[b]|} & {\lstinline|if (\(.*\)) ==> if (1==1)|} & {\lstinline|if (:[cond]) ==> if (1==1)|} &  {\lstinline|any_of ==> all_of|} & {\lstinline|any_of ==> all_of|} \\
\hline
\end{tabular}
\end{figure*}

>>>>

\begin{figure}[hbtp]
\centering
\caption{Mutation operator rule examples, using regular expressions (left) and the Comby language (right), based on parser parser combinators.}
\label{tab:rules}
  \begin{tabular}{l|l}
    \toprule
    \mc{1}{c|}{\textbf{Regexp}} & \mc{1}{c}{\textbf{Comby}}                          \\\midrule
    \mc{2}{c}{\textbf{Universal}}                         \\\midrule
    {\lstinline|< ==> >|} & {\lstinline|:[a]<:[b] ==> :[a]>:[b]|}   \\
    {\lstinline|< ==> ==|} & {\lstinline|:[a]<:[b] ==> :[a]==:[b]|} \\
    {\lstinline|< ==> <=|}  & {\lstinline|:[a]<:[b] ==> :[a]<=:[b]|} \\\midrule
\mc{2}{c}{\textbf{C-Like}} \\\midrule
 {\lstinline|else ==>|}  & {\lstinline|else ==>|} \\
 {\lstinline|if (\(.*\)) ==> if (!\1)|} &  {\lstinline|if (:[cond]) ==> if (!(:[cond]))|} \\
 {\lstinline|if (\(.*\)) ==> if (1==1)|} & {\lstinline|if (:[cond]) ==> if (1==1)|} \\
\toprule
\mc{2}{c}{\textbf{Language-Specific}} \\\midrule
 {\lstinline|synchronized ==>|} &  {\lstinline|synchronized ==>|} \\
 {\lstinline|(\^{}\s*)(\S+.*\n) ==> \1pass|} & {\lstinline|:[ s]:[expr]:[lf [\n]] ==> :[s]pass:[lf]|} \\
 {\lstinline|any_of ==> all_of|} & {\lstinline|any_of ==> all_of|} \\
\hline
\end{tabular}
\end{figure}
